The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-09-03 src/cover-letter.tex
Re-submitted version.

    Many thanks for considering our manuscript for possible publication in
    \textit{Nature Human Behavior}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership.

    We incorporate detailed NPIs, different tests, and vaccinations in an agent-based
    model. Importantly, we do so in a way that allows to calibrate its parameters based
    on routinely available data. We apply the model to the second and third waves of the
    CoViD-19 pandemic in Germany over a period of 9 months, achieving a good fit to
    actual infection rates.

    Our core substantive result is that rapid testing has been very effective relative
    to many NPIs in a low-medium vaccination environment.

    \closing{Kind regards,}

>>>>

    Many thanks for considering our manuscript for possible publication in
    \textit{scientific reports}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership. We make both methodological and substantive
    contributions.\\[0.5ex]
    We incorporate detailed NPIs, different tests, and vaccinations in an agent-based
    model, taking into account behavioural reactions to symptoms or positive test
    results. Importantly, we do so in a way that allows to calibrate its parameters
    based on routinely available data. We apply the model to the second and third waves
    of the CoViD-19 pandemic in Germany over a period of 9 months, achieving a good fit
    to actual infection rates.\\[0.5ex]
    Our core substantive result is that rapid testing has been very effective relative
    to many NPIs in a low-medium vaccination environment. This is the relevant scenario
    for most countries across the world at present; it seems also applicable to countries
    with high vaccination rates under the conditions of the delta variant.\\[0.5ex]
    A prior submission required clarification regarding the pre-print servers we had
    uploaded the paper to; see the e-mail conversation with Dr.{} Sabrya Carim. These are the links to the 
    pre-prints (all exactly the same paper):\\[-2ex]
    \begin{itemize}
        \item \href{https://arxiv.org/abs/2106.11129}{arXiv.org}\\[-2ex]
        \item \href{https://www.iza.org/publications/dp/14510/the-effectiveness-of-strategies-to-contain-sars-cov-2-testing-vaccinations-and-npis}{IZA}\\[-2ex]
        \item \href{https://www.econtribute.de/RePEc/ajk/ajkdps/ECONtribute_100_2021.pdf}{ECONtribute}\\[-2ex]
        \item \href{https://www.crctr224.de/en/research-output/discussion-papers/archive/2021/DP302}{Collaborative Research Center TR-224 Bonn/Mannheim}\\[2ex]
    \end{itemize}

    \closing{Many thanks for your consideration and please let me know should any further questions arise. Kind regards,}
